The universal property of infinite direct sums in C$^*$-categories and W$^*$-categories

### 2019-07-10 direct_sums.tex
fix

The set~\eqref{AiB} is a vector space under componentwise addition and scalar multiplication, where closure under addition follows from $f_i g^*_i + g_i f^*_i \leq f_i f^*_i + g_i g^*_i$, which holds because of $(f_i - g_i) (f^*_i - g^*_i) \geq 0$. We furthermore consider this vector space as a normed space under the norm
\[
	\| (f_i)_{i \in I} \| \ :=\  \Bigl\| \textstyle \sum_i f_i f_i^* \Bigr\|^{1/2},
\]
where the triangle inequality again follows from $f_i g^*_i + g_i f^*_i \leq f_i f^*_i + g_i g^*_i$. We interpret the sum as before either in terms of a supremum over the norm of finite partial sums, or as converging in the double dual $\cat{C}(B,B)^{**}$.

>>>>

The set~\eqref{AiB} is a vector space under componentwise addition and scalar multiplication, where closure under addition follows from $f_i g^*_i + g_i f^*_i \leq f_i f^*_i + g_i g^*_i$, which holds because of $(f_i - g_i) (f^*_i - g^*_i) \geq 0$. We furthermore consider this vector space as a normed space under the norm
\[
	\| (f_i)_{i \in I} \| \ :=\  \Bigl\| \sum_i f_i f_i^* \Bigr\|^{1/2},
\]
The triangle inequality for this norm is not directly obvious.
It follows from the following generalization of the
    Cauchy--Schwarz inequality, see e.g.~\cite[\S142\textsubscript{III \& IV}]{bas}.
\begin{equation*}
    \Bigl(\sum_i f_i g_i^*\Bigr) \Bigl(\sum_j g_j f_j^*\Bigr)
    \ \leq \ \Bigl\| \sum_i g_ig_i^* \Bigr\| \, \sum_j f_j f_j^* .
\end{equation*}
We interpret the sum as before either in terms of a supremum over the norm of finite partial sums, or as converging in the double dual $\cat{C}(B,B)^{**}$.
